Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-05-15 nips_2018.tex
supplement stuff
nicer figures and various edits

Human vision is rich -- we infer shape, objects, parts of objects,
and relations between objects -- and vision is also abstract:
we can perceive the radial symmetry of a spiral staircase,
the iterated repetition in the Ising model,
see the forest for the trees, and also the recursion within the trees.
How could we build an agent with similar visual inference abilities?
Here we
cast this problem as program learning,
and take as our goal to learn high--level
graphics programs from simple 2D drawings.
The graphics programs we consider make figures like those found in machine learning papers
(Fig.~\ref{firstPageExamples}),
and capture high-level features of a drawing like
symmetry, repetition, and reuse of structure.

@@

This two-step factoring can be framed as probabilistic inference in a generative model where a latent program
 is executed to produce a set of drawing commands,
 which are then rendered to form an image (Fig.~\ref{roadmap}).
 We refer to this set of drawing commands as a \textbf{specification (spec)} because it specifies what the graphics program drew while lacking the high-level structure determining how the program decided to draw it.
 We infer the spec from an image using stochastic search (Sequential Monte Carlo)
 and infer a program from a spec using  constraint-based program synthesis~\citep{solar2008program} --
 synthesizing structures like symmetries, loops, or conditionals.
 In practice, both stochastic search and program synthesis are
 prohibitively slow,
 and so we learn models that accelerate inference for both programs and specs,
 in the spirit of ``amortized inference''~\cite{paige2016inference},
 using a neural network to amortize the cost of inferring specs from images and using
 a variant of Bias--Optimal Search~\cite{schmidhuber2004optimal}
 to amortize the cost of synthesizing programs from specs.
 \begin{figure}[h]
  \centering\begin{tikzpicture}
  \node[ thick,anchor = west,inner sep=0pt,label={[yshift = 0.3cm]{\small \begin{tabular}{c}
          Image\\
          (Observed)
  \end{tabular}}}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
    \node[ultra thick,anchor = west,inner sep=0pt](traceSource) at (3.7,0.5){    \begin{lstlisting}[basicstyle = \scriptsize\ttfamily]
line, line,
rectangle,
line, ...
\end{lstlisting}};
    \node[ultra thick,anchor = west,inner sep=0pt](traceImage) at (4,-0.5) {
      \includegraphics[width = 0.9cm]{figures/39-parse.png}}; 
    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = above:{{\small \begin{tabular}{c}
            Spec/Drawing Commands\\
            (Latent)
    \end{tabular}}}] {};

    \node[draw, thick,anchor = west,inner sep=2pt,label=above:{\small \begin{tabular}{c}
          Program\\
          (Latent)
    \end{tabular}}](program) at (7.7,0) {
      \begin{lstlisting}
for (j < 3)
for (i < 3)
if (...)
 line(...)
 line(...)
rectangle(...)
    \end{lstlisting}};
    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (12,0.5) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
%    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Similarity}](similarity) at (11.3,0) {\includegraphics[width = 1cm]{figures/expert-38-trim.png}};
    \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (12.1,-1.2) {\small Error correction};

    \draw[->, ultra thick] (trace.west) -- node[fill = white,rotate = -90] {{\small Rendering}} (observation.east);
    \draw[->, very thick, red] ([xshift = -5]observation.south) to[out = -30,in = -150] node[midway,yshift = -6]{{\small Learning + Stochastic search}} ([xshift = -15]trace.south);
    \draw[->, ultra thick] (program.west) -- node[fill = white,rotate = -90] {{\small Execution}} (trace.east);
    \draw[->, thick, red, very thick] ([xshift = 10]trace.south) to[out = -10,in = -170] node[midway,yshift = -6]{{\small Learning + Program synthesis}} ([xshift = 10]program.south);
%    \draw[->, thick, red] (program.east) to[out = 80,in = 180] (errors.west);
%    \draw[->, thick] (program.east) to[out = 40,in = -230] (similarity.west);
    \draw[->, thick, red, very thick] (program.east) to[out = 60,in = 180] (extrapolate.west);

    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
    ([yshift = -15,xshift = -130]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Image$\to$Spec}} ([yshift = -15,xshift = -5]trace.south);
    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Spec$\to$Program}} ([xshift = 170,yshift = -15]trace.south);
    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
([xshift = 180,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 250,yshift = -15]trace.south);
  \end{tikzpicture}
  \caption{Black arrows: Top--down generative model; Program$\to$Spec$\to$Image. Red arrows: Bottom--up inference procedure.}\label{roadmap}
 \end{figure}

 The new contributions of this work are (1) a working model that can infer high-level symbolic programs from raw perceptual input, and (2) a technique for using learning to amortizing the cost of program synthesis, described in Section~\ref{learningASearchPolicy}.

@@

    \caption{Near misses. Rightmost: illusory contours (note: no SMC)}\label{drawingFailures}
  \end{minipage}

@@

\section{Synthesizing graphics programs from specs}\label{programSynthesisSection}
Although the spec describes the contents
of a scene, it does not encode higher-level features of the image
such as repeated motifs or symmetries, which are more naturally captured by a graphics program.
We seek to synthesize graphics programs from their specs.

@@

\begin{table}[t]
  \caption{Drawings (left), their specs (middle left), and programs synthesized from these specs (middle right). Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands. Note nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
%  \vspace{-0.6cm}
\centering  \begin{tabular}{m{1.5cm}llc}
    \toprule
    \textbf{Drawing}&\textbf{Spec}&\textbf{Program}&%\begin{tabular}{c}
      \textbf{Compression factor}%\\\textbf{factor}
      %      \end{tabular}\\
      \\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{lstlisting}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{lstlisting}
for(i<3)
 line(i,-1*i+6,
      2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{lstlisting}
     \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(5,13,2,10,arrow)
%% Circle(5,9)
%% Circle(8,5)
%% Line(2,8, 2,6,arrow)
%% Circle(2,5)
%% \end{lstlisting}
%% \small\emph{... etc. ...; 13 lines}
%% \end{minipage}&
%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
%% circle(4,10)
%% for(i<3)
%%  circle(-3*i+7,5)
%%  circle(-3*i+7,1)
%%  line(-3*i+7,4,-3*i+7,2,arrow)
%%  line(4,9,-3*i+7,6,arrow)
%% \end{lstlisting}
%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Circle(5,8)
Circle(2,8)
Circle(8,11)
Line(2,9, 2,10)
Circle(8,8)
Line(3,8, 4,8)
Line(3,11, 4,11)
\end{lstlisting}
  \small\emph{... etc. ...; 21 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<3)
 for(j<3)
  if(j>0)
   line(-3*j+8,-3*i+7,
        -3*j+9,-3*i+7)
   line(-3*i+7,-3*j+8,
        -3*i+7,-3*j+9)
  circle(-3*j+7,-3*i+7)
\end{lstlisting}
\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Rectangle(1,10,3,11)
Rectangle(1,12,3,13)
Rectangle(4,8,6,9)
Rectangle(4,10,6,11)
\end{lstlisting}
  \small\emph{... etc. ...; 16 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<4)
 for(j<4)
  rectangle(-3*i+9,-2*j+6,
            -3*i+11,-2*j+7)
\end{lstlisting}
\end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
%% \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(11,14,13,14,arrow)
%% Circle(10,10)
%% Line(10,13,10,11,arrow)
%% Circle(6,10)
%% \end{lstlisting}
%%     \small\emph{... etc. ...; 15 lines}
%% \end{minipage}&
%% \begin{minipage}{\exampleProgramSize}
%%     \begin{lstlisting}
%% for(i<4)
%%  line(-4*i+13,4,-4*i+13,2,arrow)
%%  for(j<3)
%%   if(j>0)
%%    circle(-4*i+13,4*j+-3)
%%   line(-4*j+10,5,-4*j+12,5,
%%        arrow)
%% \end{lstlisting}
%%   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule

@@

Given a search policy, what is the best way of using it to quickly find minimum cost programs?
We use a bias-optimal search algorithm~\citep{schmidhuber2004optimal}:

@@

\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
\begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
  \includegraphics[width = 5cm]{figures/programSuccess7.png}
  \includegraphics[width = 5cm]{figures/programSuccess16.png}
  \caption{Left: hand drawings. Center: interpretations favored by the deep network. Right: interpretations favored after learning a prior over programs. The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
\vspace{-0.75cm}  \end{wrapfigure}
The program synthesizer corrects errors made by the neural network by favoring specs which lead to more
concise or general programs.  For example, figures with perfectly aligned objects are preferable, %% to figures whose parts are slightly misaligned,
and precise alignment lends itself to short
programs.
Concretely,
we run the program synthesizer on the
Top-$k$  most likely specs output by the neurally guided sampler.
Then, the system
reranks the Top-$k$  by  the prior probability of their programs.
The prior probability of a program is learned by picking the prior maximizing
the likelihood of the ground truth specs;
see supplement for details.
But, this procedure can only correct errors when
a correct spec is in the Top-$k$.
Our sampler could only do better on
7/100 drawings by looking at the Top-100 samples
(see Fig.~\ref{drawingIntersectionOverUnion}),
precluding a statistically significant analysis of how much
learning a prior over programs could help correct errors.
But,
learning this prior does sometimes 
help correct mistakes made by the neural network; %% , and also
%% occasionally introduces mistakes of its own; 
see
Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
example of the kinds of corrections that it makes.
See supplement for details.

@@

\textbf{Program Induction:}
Our approach to learning to search for programs draws theoretical
underpinnings from Levin
search~\citep{levin1973universal,solomonoff1984optimum} and
Schmidhuber's OOPS model~\citep{schmidhuber2004optimal}.
DeepCoder~\citep{BalGauBroetal16} is a recent model which, like ours, learns to predict likely program components.
Our work differs by identifying and modeling
the trade-off between tractability and probability of success.
TerpreT~\citep{gaunt2016terpret} 
systematically compares constraint-based program synthesis techniques
against gradient-based search techniques, like those used to train
Differentiable Neural Computers~\citep{graves2016hybrid}.  The TerpreT
experiments motivate our use of constraint-based techniques.

@@

We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images. The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic specifications; it then feeds these specs to a general-purpose program synthesis engine to infer a structured graphics program. We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
More generally, we believe the problem of inferring visual programs is a promising direction for machine perception.

>>>>

Human vision is rich -- we infer shape, objects, parts of objects,
and relations between objects -- and vision is also abstract:
we can perceive the radial symmetry of a spiral staircase,
the iterated repetition in the Ising model,
see the forest for the trees, and also the recursion within the trees.
How could we build an agent with similar visual inference abilities?
As a small step in this direction, 
we cast this problem as program learning,
and take as our goal to learn high--level
graphics programs from simple 2D drawings.
The graphics programs we consider make figures like those found in machine learning papers
(Fig.~\ref{firstPageExamples}),
and capture high-level features like %of a drawing like
symmetry, repetition, and reuse of structure.

@@

This two-step factoring can be framed as probabilistic inference in a generative model where a latent program
 is executed to produce a set of drawing commands,
 which are then rendered to form an image (Fig.~\ref{roadmap}).
 We refer to this set of drawing commands as a \textbf{specification (spec)} because it specifies what the graphics program drew while lacking the high-level structure determining how the program decided to draw it.
 We infer a spec from an image using stochastic search (Sequential Monte Carlo)
 and infer a program from a spec using  constraint-based program synthesis~\citep{solar2008program} --
 synthesizing structures like symmetries, loops, or conditionals.
 In practice, both stochastic search and program synthesis are
 prohibitively slow,
 and so we learn models that accelerate inference for both programs and specs,
 in the spirit of ``amortized inference''~\cite{paige2016inference},
 training a neural network to amortize the cost of inferring specs from images and using
 a variant of Bias--Optimal Search~\cite{schmidhuber2004optimal}
 to amortize the cost of synthesizing programs from specs.
 \begin{figure}[h]
  \centering\begin{tikzpicture}
  \node[ thick,anchor = west,inner sep=0pt,label={[yshift = 0.3cm]{\small \begin{tabular}{c}
          \textbf{Image}\\
          \textbf{(Observed)}
  \end{tabular}}}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
    \node[ultra thick,anchor = west,inner sep=0pt](traceSource) at (3.7,0.5){    \begin{lstlisting}[basicstyle = \scriptsize\ttfamily]
line, line,
rectangle,
line, ...
\end{lstlisting}};
    \node[ultra thick,anchor = west,inner sep=0pt](traceImage) at (4,-0.5) {
      \includegraphics[width = 0.9cm]{figures/39-parse.png}}; 
    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = above:{{\small \begin{tabular}{c}
            \textbf{Spec/Drawing Commands}\\
            \textbf{(Latent)}
    \end{tabular}}}] {};

    \node[draw, thick,anchor = west,inner sep=2pt,label=above:{\small \begin{tabular}{c}
          \textbf{Program}\\
          \textbf{(Latent)}
    \end{tabular}}](program) at (7.7,0) {
      \begin{lstlisting}
for (j < 3)
for (i < 3)
if (...)
 line(...)
 line(...)
rectangle(...)
    \end{lstlisting}};
    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (12,0.5) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
%    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Similarity}](similarity) at (11.3,0) {\includegraphics[width = 1cm]{figures/expert-38-trim.png}};
    \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (12.1,-1.2) {\small Error correction};

    \draw[->, ultra thick] ([yshift=10]trace.west) to[out = 150,in = 30] node[midway,yshift = 6]{{\small Rendering}} ([xshift=5,yshift=10]observation.east); % -- node[fill = white,rotate = -90] {{\small Rendering}}
    \draw[->, very thick, red] ([yshift = -15,xshift=3]observation.east) to[out = -30,in = -150] node[midway,yshift = -12,xshift=5]{{\small \begin{tabular}{l}
          Learning + \\Stochastic search
    \end{tabular}}} ([yshift = -15]trace.west);
    \draw[->, ultra thick] ([yshift=10]program.west) to[out = 150,in = 30] node[midway,yshift = 6] {{\small Execution}} ([yshift=10]trace.east);
    \draw[->, very thick, red] ([yshift = -15,xshift=0]trace.east) to[out = -30,in = -150] node[midway,yshift = -12,xshift=9]{{\small \begin{tabular}{l}
          Learning + \\Program synthesis
    \end{tabular}}} ([yshift = -15]program.west);

%    \draw[->, thick, red, very thick] ([xshift = 10]trace.south) to[out = -10,in = -170] node[midway,yshift = -6]{{\small Learning + Program synthesis}} ([xshift = 10]program.south);
%    \draw[->, thick, red] (program.east) to[out = 80,in = 180] (errors.west);
%    \draw[->, thick] (program.east) to[out = 40,in = -230] (similarity.west);
    \draw[->, thick, red, very thick] (program.east) to[out = 60,in = 180] (extrapolate.west);

    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
    ([yshift = -11,xshift = -130]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Image$\to$Spec}} ([yshift = -11,xshift = -5]trace.south);
    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
    ([xshift = 5,yshift = -11]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Spec$\to$Program}} ([xshift = 170,yshift = -11]trace.south);
    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
([xshift = 180,yshift = -11]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 255,yshift = -11]trace.south);
  \end{tikzpicture}
  \caption{Black arrows: Top--down generative model; Program$\to$Spec$\to$Image. {\color{red}Red} arrows: Bottom--up inference procedure. \textbf{Bold:} Random variables (image/spec/program)}\label{roadmap}
 \end{figure}

 The new contributions of this work are (1) a working model that can infer high-level symbolic programs from perceptual input, and (2) a technique for using learning to amortize the cost of program synthesis, described in Section~\ref{learningASearchPolicy}.

@@

    \caption{Near misses. Rightmost: illusory contours (note: no SMC in rightmost)}\label{drawingFailures}
  \end{minipage}

@@

\section{Synthesizing graphics programs from specs}\label{programSynthesisSection}
Although the spec describes the contents
of a scene, it does not encode higher-level features of an image
such as repeated motifs or symmetries, which are more naturally captured by a graphics program.
We seek to synthesize graphics programs from their specs.

@@

\begin{table}[t]
  \caption{Drawings (left), their specs (middle left), and programs synthesized from those specs (middle right). Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands. Note the nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
%  \vspace{-0.6cm}
\centering  \begin{tabular}{m{1.5cm}llc}
    \toprule
    \textbf{Drawing}&\textbf{Spec}&\textbf{Program}&%\begin{tabular}{c}
      \textbf{Compression factor}%\\\textbf{factor}
      %      \end{tabular}\\
      \\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{lstlisting}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{lstlisting}
for(i<3)
 line(i,-1*i+6,
      2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{lstlisting}
     \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(5,13,2,10,arrow)
%% Circle(5,9)
%% Circle(8,5)
%% Line(2,8, 2,6,arrow)
%% Circle(2,5)
%% \end{lstlisting}
%% \small\emph{... etc. ...; 13 lines}
%% \end{minipage}&
%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
%% circle(4,10)
%% for(i<3)
%%  circle(-3*i+7,5)
%%  circle(-3*i+7,1)
%%  line(-3*i+7,4,-3*i+7,2,arrow)
%%  line(4,9,-3*i+7,6,arrow)
%% \end{lstlisting}
%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Circle(5,8)
Circle(2,8)
Circle(8,11)
Line(2,9, 2,10)
Circle(8,8)
Line(3,8, 4,8)
Line(3,11, 4,11)
\end{lstlisting}
  \small\emph{... etc. ...; 21 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<3)
 for(j<3)
  if(j>0)
   line(-3*j+8,-3*i+7,
        -3*j+9,-3*i+7)
   line(-3*i+7,-3*j+8,
        -3*i+7,-3*j+9)
  circle(-3*j+7,-3*i+7)
\end{lstlisting}
\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Rectangle(1,10,3,11)
Rectangle(1,12,3,13)
Rectangle(4,8,6,9)
Rectangle(4,10,6,11)
\end{lstlisting}
  \small\emph{... etc. ...; 16 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<4)
 for(j<4)
  rectangle(-3*i+9,-2*j+6,
            -3*i+11,-2*j+7)
\end{lstlisting}
\end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
%% \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(11,14,13,14,arrow)
%% Circle(10,10)
%% Line(10,13,10,11,arrow)
%% Circle(6,10)
%% \end{lstlisting}
%%     \small\emph{... etc. ...; 15 lines}
%% \end{minipage}&
%% \begin{minipage}{\exampleProgramSize}
%%     \begin{lstlisting}
%% for(i<4)
%%  line(-4*i+13,4,-4*i+13,2,arrow)
%%  for(j<3)
%%   if(j>0)
%%    circle(-4*i+13,4*j+-3)
%%   line(-4*j+10,5,-4*j+12,5,
%%        arrow)
%% \end{lstlisting}
%%   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule

@@

Given a search policy, what is the best way of using it to quickly find minimum cost programs?
We use a bias-optimal search algorithm (c.f. Schmidhuber 2004~\citep{schmidhuber2004optimal}):

@@

\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
\begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
  \includegraphics[width = 5cm]{figures/programSuccess7.png}
  \includegraphics[width = 5cm]{figures/programSuccess16.png}
  \caption{Left: hand drawings. Center: interpretations favored by the deep network. Right: interpretations favored after learning a prior over programs. The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
\vspace{-0.75cm}  \end{wrapfigure}
The program synthesizer corrects errors made by the neural network by favoring specs which lead to more
concise or general programs.  For example, figures with perfectly aligned objects are preferable, %% to figures whose parts are slightly misaligned,
and precise alignment lends itself to short
programs.
Concretely,
we run the program synthesizer on the
Top-$k$  most likely specs output by the neurally guided sampler.
Then, the system
reranks the Top-$k$  by  the prior probability of their programs.
The prior probability of a program is learned by optimizing the parameters of the prior so as to maximize
the likelihood of the ground truth specs;
see supplement for details.
But, this procedure can only correct errors when
a correct spec is in the Top-$k$.
Our sampler could only do better on
7/100 drawings by looking at the Top-100 samples
(see Fig.~\ref{drawingIntersectionOverUnion}),
precluding a statistically significant analysis of how much
learning a prior over programs could help correct errors.
But,
learning this prior does sometimes 
help correct mistakes made by the neural network; %% , and also
%% occasionally introduces mistakes of its own; 
see
Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
example of the kinds of corrections that it makes.
See supplement for details.

@@

\textbf{Program Induction:}
Our approach to learning to search for programs draws theoretical
underpinnings from Levin
search~\citep{levin1973universal,solomonoff1984optimum} and
Schmidhuber's OOPS model~\citep{schmidhuber2004optimal}.
DeepCoder~\citep{BalGauBroetal16} is a recent model which, like ours, learns to predict likely program components.
Our work differs by identifying and modeling
the trade-off between tractability and probability of success.
TerpreT~\citep{gaunt2016terpret} 
systematically compares constraint-based program synthesis techniques
against gradient-based search methods, like those used to train
Differentiable Neural Computers~\citep{graves2016hybrid}.  The TerpreT
experiments motivate our use of constraint-based techniques.

@@

We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images. The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic specifications; it then feeds these specs to a general-purpose program synthesis engine to infer a structured graphics program. We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
